---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tukey2matrix

<!-- badges: start -->
<!-- badges: end -->

tukey2matrix contains one primary function `tukey_to_matrix`. The main goal of `tukey_to_matrix()` is to take the output of a `TukeyHSD()` function and convert it into a reader-friendly matrix array and comes with an option to substitute statistically significant observation with "*" for user scanning of data. 

## Installation

You can install the development version of tukey2matrix from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2022/Assignment_B1_B2_Jerry_He/tukey2matrix")
```


## Example

This a basic example of `tukey_to_matrix()` usage:

```{r example}
# Load the package
library(tukey2matrix)

# First perform an ANOVA on data from the iris dataset
AOV_Out <- aov(Petal.Length ~ Species, iris)

# Perform a TukeyHSD() test on the ANOVA analysis
TukeyHSD_Out <- TukeyHSD(AOV_Out)

# Use tukey_to_matrix() to convert the TukeyHSD() output to a user-friendly format
tukey_to_matrix(tukey_object = TukeyHSD_Out, element = Species)

# Use tukey_to_matrix() to convert the TukeyHSD() output to a user-friendly format, substituting statistically significant values with asterisks "*"
tukey_to_matrix(TukeyHSD_Out, Species, significance = FALSE)
```
